Increasing Productivity Amid Stable Nutrient Regimes in Rhode Island Lakes and Reservoirs

### 2019-05-15 manuscript/manuscript.Rmd
sentence or two added to discussion

As previously mentioned, both temperature and chlorophll *a* show increasing trends from 1993 to 2016 in Rhode Island lakes and reservoirs, while total nutrients and the nitrogen:phosphorus ratio are all relatively stable.  These stable nutrient regimes may be partly explained by

- Parameter by parameter discussion of trends
- Local scale vs Regional/Global scale
    - Why diffs?  
        - LULC?
        - Different trends
- Other trends?
    - monthly/seasonal
    - How do trends break down by trophic state?

>>>>

As previously mentioned, both temperature and chlorophll *a* show increasing trends from 1993 to 2016 in Rhode Island lakes and reservoirs, while total nutrients and the nitrogen:phosphorus ratio are all relatively stable.  These stable nutrient regimes may be partly explained by efforts to curb nutrient loadings (e.g., [Need References Here]).  Additionally, these results point to the fact that productivity is driven by processes operating at different scales.  For instance, controlling for nutrients is largely a local to watershed scale effort; whereas, warming lakes are driven by broader, climate patterns.

- Other trends?
    - monthly/seasonal
    - How do trends break down by trophic state?
